An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-14 EconGrowth-R-Functions.Rnw
Now using melt to reshape the data for graphs of lambda, alpha, beta, and SSE vs. gamma for CDe parameter estimation. Creating a lattice graph of the same variables.

<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************************************************************
  eval=FALSE,
  # ********************************************************************************************************
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
)

@@

#############################
# This function creates a series of graphs for Cobb-Douglas with energy functions
# showing various parameters as a function of gamma.
##
cdeGridGraphs <- function(countryAbbrev, energyType){
  gammaGrid <- seq(0.0, 0.95, by=0.05)
  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
  with(data, plot(gamma, SSE))
  with(data, plot(gamma, lambda))
  with(data, plot(gamma, alpha))
  with(data, plot(gamma, beta))
  with(data, plot(beta, SSE))
}

>>>>

<<setup_parent, echo=FALSE, message=FALSE, eval=TRUE>>=
require(knitr)
require(lattice)
require(latticeExtra)
require(ggplot2)
require(car)
require(mosaic)
require(xtable)
require(nlmrt)
require(micEconCES)
require(reshape2) # Provides access to data melting. See http://cran.r-project.org/web/packages/reshape2/reshape2.pdf
# tikz allows use of LaTeX formatting and font in graphs. Allows for a consistent look across the paper.
# See http://r-forge.r-project.org/R/?group_id=440 for instructions on installing tikzDevice.
require(tikzDevice) 
trellis.par.set(theme=theme.mosaic())
options(width=75)
options(show.signif.stars=TRUE)
opts_chunk$set(
  # ********************************************************************************************************
  eval=FALSE,
  # ********************************************************************************************************
  dev='tikz',    #Allows LaTeX code in graphical output. E.g., "$y$" for a variable name in the legend for a graph.
  tidy=FALSE,
  comment=NA,
  #Tells whether to cache output from chunks are saved. Cacheing saves time. 
  #However, references to LaTeX tables DO NOT WORK if cacheing is turned on (i.e., cache=TRUE).
  cache=FALSE,
  warning=FALSE,  #Tells whether to show warnings in the output.
  message=FALSE, #Turns off messages for all chunks. Set TRUE on an individual chunk to see it.
  echo=FALSE     #Tells whether to echo code for all chunks. Set TRUE on an individual chunk to see its code.
)

@@

#############################
# This function creates a series of graphs for Cobb-Douglas with energy functions
# showing various parameters as a function of gamma.
##
cdeGridGraphs <- function(countryAbbrev, energyType){
  gammaGrid <- seq(0.0, 0.95, by=0.05)
  data <- cdeGridData(countryAbbrev, energyType, gammaGrid)
  # Now melt the data so that it is in the correct form.

#   with(data, plot(gamma, SSE))
#   with(data, plot(gamma, lambda))
#   with(data, plot(gamma, alpha))
#   with(data, plot(gamma, beta))
  with(data, plot(beta, SSE))

  data_molten <- melt(data, id="gamma")
print(data_molten)

  graph <- xyplot(value ~ gamma | variable, data=data_molten,
#                 type=graphType,
#                 index.cond=indexCond, #orders the panels.
#                 layout=layout, #indicates a 3x3 arrangement of panels.
#                 strip = strip.custom(factor.levels=factorLevels, 
#                                      bg="transparent", # Sets background transparent to match the graph itself.
#                                      par.strip.text=list(cex=textScaling) # Scales text in the strip.
#                                      ),
#                 as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
#                 lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
#                 pch = symbols, col.symbol = colors, #Controls symbol parameters
#                 key=list(text=list(c("Actual", "No energy", "With $q$", "With $x$", "With $u$")),
#                          type=graphType,
#                          cex=keyTextSize * textScaling, #controls size of text in the key
#                          lines=list(lty=lineTypes, lwd=lineWidths), #controls line types
#                          pch=symbols, col=colors, #controls symbol (plot characters) types
#                          columns=keyColumns, x=keyXLoc, y=keyYLoc), #controls columns and position of the key
#                 scales=list(cex=scaleTextSize * textScaling, #controls text size on scales.
#                             tck=scaleTickSize, #controls tick mark length. < 0 for inside the graph.
#                             x=list(at=timeTics),
#                             y=list(relation="free",  #allows each axis to be different
#                                    at=yTicsForIndexedGraphs)), #specifies location for tics
#                 ylim=yLimits, #y axis limits
#                 #axis labels and scaling
#                 xlab=list(label="", cex=textScaling), 
#                 ylab=list(label="Indexed (1980=1 or 1991=1)", cex=textScaling)
                )
  return(graph)
}
